Multi-level modeling with Openflexo/\FML

### 2022-02-23 6-modelpresentation.tex
proper use of -, --, --- and $-$

The Base metamodel is completed with some behaviors implementing an execution
semantics for the executed processes. All tasks -- instantiated from
\texttt{TaskType} for a given enacted process -- manage a status. This status
is either \texttt{Not startable} (when not assigned to a performing actor or
when required input artifacts are not available), \texttt{Startable},
\texttt{Started}, \texttt{Completable} (when all output artifacts are ready) or
\texttt{Completed}. A \texttt{Task} also manages a set of performing actors, a
begin and end date, some used and produced artifacts. The \texttt{Gateway}
business logic has also been implemented through the implementation of an
abstract \texttt{execute(Process)} behavior. The management of artifacts whose
semantics follows rules defined in Sect.~\ref{sec:ProcessEnactment} (\textbf{P13}) is also implemented.

@@

The left of the figure presents the \textit{ProcessType graphical editor}.
\texttt{ProcessTypeEditor} is modeled as a virtual model declaring two model
slots (represented with bold circles). The first model slot references an
instance of Acme metamodel, while the second model slot references an instance
of diagram, conforms to the \textit{ProcessType diagram
specification}\footnote{a diagram \enquote{metamodel} which defines and specify
structure and graphical representations for edited items}. When executed, this
tool manages a graphical view for an instance of Acme metamodel (the
\textit{Acme model}) and a specific \texttt{ProcessType} instance. This tool
allows representing and editing a \texttt{ProcessType}. The highly reflective
nature of \FML and its tooling should be noted. When the drag and drop
interactor is applied for a new item, the tool allows choosing the concept type
to be instantiated. For example, when a \texttt{TaskType} is created, the user
must choose a concept inheriting from \texttt{TaskType} -- in Acme use case it
can be \texttt{SETaskTask} or \texttt{CodingTaskType} or default value
\texttt{TaskType}).

>>>>

The Base metamodel is completed with some behaviors implementing an execution
semantics for the executed processes. All tasks --- instantiated from
\texttt{TaskType} for a given enacted process --- manage a status. This status
is either \texttt{Not startable} (when not assigned to a performing actor or
when required input artifacts are not available), \texttt{Startable},
\texttt{Started}, \texttt{Completable} (when all output artifacts are ready) or
\texttt{Completed}. A \texttt{Task} also manages a set of performing actors, a
begin and end date, some used and produced artifacts. The \texttt{Gateway}
business logic has also been implemented through the implementation of an
abstract \texttt{execute(Process)} behavior. The management of artifacts whose
semantics follows rules defined in Sect.~\ref{sec:ProcessEnactment} (\textbf{P13}) is also implemented.

@@

The left of the figure presents the \textit{ProcessType graphical editor}.
\texttt{ProcessTypeEditor} is modeled as a virtual model declaring two model
slots (represented with bold circles). The first model slot references an
instance of Acme metamodel, while the second model slot references an instance
of diagram, conforms to the \textit{ProcessType diagram
specification}\footnote{a diagram \enquote{metamodel} which defines and specify
structure and graphical representations for edited items}. When executed, this
tool manages a graphical view for an instance of Acme metamodel (the
\textit{Acme model}) and a specific \texttt{ProcessType} instance. This tool
allows representing and editing a \texttt{ProcessType}. The highly reflective
nature of \FML and its tooling should be noted. When the drag and drop
interactor is applied for a new item, the tool allows choosing the concept type
to be instantiated. For example, when a \texttt{TaskType} is created, the user
must choose a concept inheriting from \texttt{TaskType} (in Acme use case it
can be \texttt{SETaskTask} or \texttt{CodingTaskType} or default value
\texttt{TaskType}).
